### 2020-01-20 types2020abstract/abstract.tex
small fixes

\textbf{Self-describing signatures}. In the current work, we
would also like to streamline and make more rigorous the specification of
signatures. Previous descriptions of GATs \cite{gat, sterling2019algebraic} used
raw syntax with well-formedness relations to describe signatures, which is
rather unwieldy to formally handle. Also, the precursor of the current work
\cite{kaposi2019constructing} used an ad-hoc QIIT to describe signatures, which
did not have a model theory worked out, and its existence was simply assumed.

In contrast, equipped with large elimination and self-description, we are able
to specify signatures and develop a model theory for signatures, without ever
using raw syntax or assuming the existence of a particular QIIT. We do the
following in order.
\begin{enumerate}
  \item
  We specify a notion of model for the theory of signatures (ToS); this is a
  category with family (CwF) extended with several type formers, allowing to
  represent a signature as a typing context, with types specifying various
  constructors.
  \item We say that a signature is a context in an \emph{arbitrary} model, i.e.
  a function with type $(M : \mathsf{ToS})\to\mathsf{Con}_M$. This can be
  viewed as a fragment of a Church-encoding; here we do not care about
  encoding the whole syntax of ToS, nor the initiality of the syntax, we only
  need a representation of signatures and the ability to interpret a signature in
  a $\mathsf{ToS}$-model.
  \item We give a semantics for signatures, as a particular $M : \mathsf{ToS}$
    model which interprets each CwF context $\Gamma$ as a structured category of
    $\Gamma$-algebras.
  \item We give a (large, infinitary) signature for $\mathsf{ToS}$ itself, such
    that interpreting the signature in the semantic model yields a structured
    category of $\mathsf{ToS}$-algebras.
\end{enumerate}
In the above construction, everything is appropriately indexed with universe
levels (we omit the details), and there is a ``bump'' of levels at every
instance of self-description.

>>>>

\textbf{Self-describing signatures}. In the current work, we
would also like to streamline and make more rigorous the specification of
signatures. Previous descriptions of GATs \cite{gat, sterling2019algebraic} used
raw syntax with well-formedness relations to describe signatures, which is
rather unwieldy to handle formally. Also, the precursor of the current work
\cite{kaposi2019constructing} used an ad-hoc QIIT to describe signatures, which
did not have a model theory worked out, and its existence was simply assumed.

In contrast, equipped with large elimination and self-description, we are able
to specify signatures and develop a model theory for signatures, without ever
using raw syntax or assuming the existence of a particular QIIT. We do the
following in order.
\begin{enumerate}
  \item
  We specify a notion of model for the theory of signatures ($\ToS$); this is a
  category with family (CwF) extended with several type formers, allowing to
  represent a signature as a typing context, with types specifying various
  constructors.
  \item We say that a signature is a context in an \emph{arbitrary} model, i.e.
  a function with type $(M : \mathsf{ToS})\to\mathsf{Con}_M$. This can be
  viewed as a fragment of a Church-encoding; here we do not care about
  encoding the whole syntax of $\ToS$, nor the initiality of the syntax, we only
  need a representation of signatures and the ability to interpret a signature in
  a $\mathsf{ToS}$-model.
  \item We give a semantics for signatures, as a particular $M : \mathsf{ToS}$
    model which interprets each CwF context $\Gamma$ as a structured category of
    $\Gamma$-algebras.
  \item We give a (large, infinitary) signature for $\mathsf{ToS}$ itself, such
    that interpreting the signature in the semantic model yields a structured
    category of $\mathsf{ToS}$-algebras.
\end{enumerate}
In the above construction, everything is appropriately indexed with universe
levels (we omit the details), and there is a ``bump'' of levels at every
instance of self-description.
